A Data-Driven Early Warning System for Mining Accidents

### 2017-03-29 San Antonio/slides/presentation_slides.Rmd
final presentation and src

---
title: "A Data-Driven Early Warning System for Mining Accidents"
shorttitle: "Mining Accident Data Analysis"
author: |
  | Yu Luo, Ashutosh Nanda, Shivaram Rajgopal, Vinay Ramesh,
  | Zhizun Zhang, Catherine Zhao, and Venkat Venkatasubramanian
shortauthor: "Luo et al."
institute: |
  | Chemical Engineering, Computer Science, and Business School
  | Columbia University
shortinstitute: "Columbia University"
date: "3/27/2017"
output: 
  beamer_presentation:
    keep_tex: false
    incremental: false
    template: rmd_template.tex
    fig_height: 4.75
    # fig_width: 4
    toc: true
    slide_level: 2
    includes:
      in_header: rmd_header.tex
---

@@

```{r new-era-num-days-lost}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
head(
  complete.active.quarters %>% filter(active) %>% arrange(desc(num.days.lost)) %>% select(
    mine.name, year, quarter, num.days.lost
  )
, 10)
```

@@

- Apply $k$-means clustering to consolidated data on all 20 features
- 3 clusters: `low`-risk, `mid`-risk, and `high`-risk
- Selected cluster centers (omitting 15 features)

```{r k-means}
if(!exists("clustering")){load("./San Antonio/output/results_markov.RData")}
sorted.cluster.centers <- clustering$centers[cluster.to.risk.label,c("num.days.lost", "num.days.restrict", "num.death", "num.dis", "viol.quantity")]
rownames(sorted.cluster.centers) <- risk.labels
print(sorted.cluster.centers)
```

>>>>

---
title: "A Data-Driven Early Warning System for Mining Accidents"
shorttitle: "Mining Accident Data Analysis"
author: |
  | Yu Luo, Ashutosh Nanda, Shivaram Rajgopal, Vinay Ramesh,
  | Zhizun Zhang, Catherine Zhao, and Venkat Venkatasubramanian
shortauthor: "Luo et al."
institute: |
  | Chemical Engineering, Computer Science, and Business School
  | Columbia University
shortinstitute: "Columbia University"
date: "3/27/2017"
output: 
  beamer_presentation:
    keep_tex: true
    incremental: false
    template: rmd_template.tex
    fig_height: 4.75
    # fig_width: 4
    toc: true
    slide_level: 2
    includes:
      in_header: rmd_header.tex
---

@@

```{r new-era-num-days-lost}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
head(
  complete.active.quarters %>% filter(active) %>% arrange(desc(num.days.lost)) %>% select(
    mine.name, year, quarter, num.days.lost
  ) %>% rename(days.lost = num.days.lost)
, 10)
```

@@

- Apply $k$-means clustering to consolidated data on all 20 features
- 3 clusters: `low`-risk, `mid`-risk, and `high`-risk
- Selected cluster centers (omitting 17 features)

```{r k-means}
if(!exists("clustering")){load("./San Antonio/output/results_markov.RData")}
sorted.cluster.centers <- clustering$centers[cluster.to.risk.label,c("num.days.lost", "num.days.restrict", "num.death")]#, "num.dis", "viol.quantity")]
rownames(sorted.cluster.centers) <- risk.labels
print(sorted.cluster.centers)
```
